Blockchain System

### 2020-10-20 papers/execution-model/model.tex
further consolidation

\section{Definitions}
\begin{definition}[Set]
Let $\mathbf{Elt}$ be the set of (concrete) elements. Let $\emptyset$ be an empty set and $\mathbf{e}$ $\in$  $\mathbf{Elt}$. A set of elements is expressed as the following syntax:
\\
$\mathbf{s} :: = \emptyset \mid \mathbf{e} \mid \mathbf{s :: s}$
\end{definition}

\begin{definition}[Account]
An account is a tuple $\langle \ALS, \PAK, \PUK, \PKH \rangle $, where $\ALS$ is the alias of the account, $\PAK$ is its private key, $\PUK$ is its public key and $\PKH$ is its public key hash . 
\end{definition}

\begin{definition}[Contract]
An contract is a tuple $\langle  \ALS, \PUH, \CODE \rangle $, where
$\ALS$ is the alias of the contract, $\PUH$ is its public hash, and
$\CODE$ is the code of the contract. 
\end{definition}

\begin{definition}[Manager]
A manager manages a single account. It is represented by a
tuple $\langle  \PUK, \PKH, \BAL, \COU \rangle $, where  $\PUK$ is the
public key of an account, $\PKH$ is its public key hash, $\BAL$ is its
balance and $\COU$ is its counter whose form is a pair $(n, b)$, where $n$ is a natural number and ${b}$
is a boolean value.  
\end{definition}

\begin{definition}[Contractor]
  A contractor manages a smart contract. It is
  represented by a tuple
  $\langle \PUH, \BAL, \CODE, \STORAGE \rangle $, where $\PUH$ is the
  public key hash of the contract, $\BAL$ is its current balance, $\CODE$ is its
  code, and $\STORAGE$ is its current storage.
\end{definition}

\begin{definition}[Operation]
  Operations are defined by the following grammar:
  \begin{align*}
    \OP &::= \TRANSFER[\STRING]\NTEZ\PKH{\PKH'}\MTEZ
    \\&\mid \ORIGINATE\ID\NTEZ\PKH\CODE\STRING\MTEZ
    % \\&\mid transfer $\mathbf{n}$ from $\PKH$ to  $\PUH$ arg $\mathbf{s}$ fee $\mathbf{m}$
  \end{align*}
%\\$\mid$ register key $\PKH$ as delegate fee $\mathbf{m}$ 
%\\$\mid$ set delegate for $\PKH$ to $\PKH'$  fee $\mathbf{m}$ 
%\\$\mid$ withdraw delegate from $\PKH$ fee $\mathbf{m}$ 
\end{definition}

\begin{definition}[Query]
Queries are defined by the following grammar:
\begin{align*}
  \QRY & ::= \GETBALANCE {\PKH / \PUH}
  \\&\mid \GETSTATUS\OPH
  \\&\mid \GETSTORAGE\PUH
  \\&\mid \GETCODE\PUH 
  \\&\mid \GETPUBLICKEY\PKH
  \\&\mid \GETCOUNTER\PKH
\end{align*}

@@

\end{definition}
 \begin{definition}[State of a node]
   The state of a node is a tuple
   $\NODE = [\ACCOUNTS, \OPERATIONS, \CONTRACTS]$ where $\ACCOUNTS$ is a set of accounts,
   $\OPERATIONS$ a set of operations, and $\CONTRACTS$  a set of contracts. 
\end{definition}

When an operation is injected in a node, it enters a \emph{pending pool}
(and is called a \emph{pending operation}). 
 \begin{definition}[Pending operation]
A pending operation is a tuple  $\langle  \OP, \OPH, \TIME
\rangle $, where $\OP$ is an operation, $\OPH$ is the operation hash,
and $\TIME$ is the time when the operation was injected. 
\end{definition}
After some time, a pending operation may be included in the blockchain as an accepted operation.
%Let \textit{P} is the set of pending operations.
 \begin{definition}[Accepted operation]
An accepted operation  is a tuple $\langle  \OP, \OPH, \TIME \rangle
$, where $\OP$ is an operation, $\OPH$ is the operation hash, and
$\TIME$ is the time when it was included in the blockchain. 
\end{definition}

\begin{definition}[Blockchain]
  The state of a blockchain is a tuple
  $[\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$ where
  $\PENDING$ is a set of pending operations,  $\ACCEPTED$ is a set
  of accepted operations, $\MANAGERS$ is a set of managers,
  $\CONTRACTORS$ is a set of contractors, and $\TIME$ is the current time. 
\end{definition}

\begin{definition}[Blockchain system]
A blockchain system is a pair
$ \NODE \| \BLOCKCHAIN$ where
\fxnote[inline]{Should the model contain multiple nodes?}
\begin{enumerate}
\item $\NODE = [\ACCOUNTS, \OPERATIONS, \CONTRACTS]$ is the state of a node, and
\item $\BLOCKCHAIN = [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$ is the state of a blockchain 
  such that $\forall c \in \ACCOUNTS \implies \exists k\in \MANAGERS, k.\PKH = c.\PKH$
  and $\forall s \in \CONTRACTS \implies \exists p \in \CONTRACTORS, s.\PUH = p.\PUH$.
\end{enumerate}
\end{definition}

\section{Rules}

@@

\begin{mathpar}
  \inferrule[Node-Transfer]
  {\CHECKACC (\PUK, \ACCOUNTS)
  }{
    [\ACCOUNTS, \OPERATIONS, \CONTRACTS]
    \NodeTrans
    [\ACCOUNTS, (\TRANSFER\NTEZ\PUK{\PUK'}\MTEZ) :: \OPERATIONS, \CONTRACTS]
  }

  \inferrule[Node-Originate]
  {\CHECKACC (\PUK, \ACCOUNTS) \\
    \CHECKID (\ID, \CONTRACTS)
  }{
    [\ACCOUNTS, \OPERATIONS, \CONTRACTS]
    \NodeTrans \\
    [\ACCOUNTS, (\ORIGINATE\ID\NTEZ\PUK\CODE\STRING\MTEZ) :: \OPERATIONS, \CONTRACTS]
  }

  \inferrule[Node-System]
  {\NODE \NodeTrans \NODE'}
  { {\NODE \| \BLOCKCHAIN} \SystemTrans {\NODE'\| \BLOCKCHAIN}}
\end{mathpar}

@@

\begin{equation}{}
\frac{\text{$\neg$ checkPub(\MANAGERS, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow$ }\\
\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 6 [included]:
\begin{mathpar}
  \inferrule[Block-Accept]{
    % \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
    \TIME'-\TIME < 60
  }{
    {[\Angle{\OP,\OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
      \CONTRACTORS, \TIME']} \rightarrow 
    {[\PENDING, \Angle{\OP,\OPH,\TIME'} :: \ACCEPTED, \MANAGERS,
      \CONTRACTORS, \TIME'+1]}
  }
\end{mathpar}
Rule 7 [timeout]:
\begin{mathpar}
  \inferrule[Block-Timeout]{
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
    \TIME'-\TIME \ge 60
  }{
    {[\Angle{\OP,\OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
      \CONTRACTORS, \TIME']} \rightarrow 
    {[\PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS, \PUK, \FALSE),
      \CONTRACTORS, \TIME']}
  }
\end{mathpar}

@@

\begin{mathpar}
  \inferrule[Block-Originate]{
    \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
    \CHECKCOU (\MANAGERS, \PUK) \\
    \CHECKPRG (\CODE, \STRING) \\\\
    \ORIG = \ORIGINATE\ID\NTEZ\PUK\CODE\STRING\MTEZ 
  }{
    \Angle{[
      \ACCOUNTS, \ORIG :: \OPERATIONS, \CONTRACTS
      ], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]} \to \\
    \Angle{[\ACCOUNTS, \OPERATIONS, \CONTRACTS],
      [\ORIG :: \PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS,\PUK,\TRUE), \CONTRACTORS, \TIME]}
  }
\end{mathpar}
% \begin{equation}{}
% \frac{\text{checkBal(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ \text{checkPrg($code, s$)}}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{ :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] $\rangle \rightarrow \langle$ [\ACCOUNTS, \OPERATIONS, \CONTRACTS],} \text{[(originate contract ${id}$ transferring ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: \PENDING, \ACCEPTED, updateCou(\MANAGERS, $pkh$, True), \CONTRACTORS, \TIME] $\rangle$}}} 
% \end{equation}
~\\
~\\
Rule 3 [rejected of code]:

@@

\begin{equation}{}
\frac{\text{$\neg$ checkBal(\MANAGERS, $pkh, n, m$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow \langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS],} \text{[\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 6 [included]:
\begin{equation}{}
\frac{}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [$<$ (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running } \\
\text{${code}$ init ${s}$), \TIME $>$ :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ]$\rangle \rightarrow \langle$[\ACCOUNTS, \OPERATIONS,($< id$, } \\
\text{generateHash($id, code, s$, \TIME'), $code >$ :: \CONTRACTS)], [\PENDING, $<$ (originate contract ${id}$ } \\
\text{transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$), \TIME' $>$ :: \ACCEPTED, updateSucc(\MANAGERS, } \\
\text{$puk, n, m$), ($<$ generateHash($id, code, s$, \TIME'), $n, code$, } \\
 \text{getStorage($code, s$) $>$) :: \CONTRACTORS), \TIME' + 1]$\rangle$}}} 
\end{equation}
~\\
Rule 7 [timeout]:
\begin{equation}{}
\frac{\text{\TIME' - \TIME $\ge$ 60}}{\parbox{4.2in}{\text{[$<$ (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$) $>$ } \\
\text{:: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ] $\rightarrow$[\PENDING, \ACCEPTED, updateCou(\MANAGERS, $puk$, False), \CONTRACTORS, \TIME']}}} 
\end{equation}
~\\
~\\
B. \textbf{Transfer}
\\
~\\
Rule 1 [proposal]:

>>>>

\section{Definitions}
\begin{definition}%[Set]
Let $\mathbf{Elt}$ be the set of (concrete) elements. Let $\emptyset$ be an empty set and $\mathbf{e}$ $\in$  $\mathbf{Elt}$. A set of elements is expressed as the following syntax:
\\
$\mathbf{s} :: = \emptyset \mid \mathbf{e} \mid \mathbf{s :: s}$
\end{definition}

\begin{definition}%[Account]
An \emph{account} is a tuple $\langle \ALS, \PAK, \PUK, \PKH \rangle $, where $\ALS$ is the alias of the account, $\PAK$ is its private key, $\PUK$ is its public key and $\PKH$ is its public key hash . 
\end{definition}

\begin{definition}%[Contract]
An \emph{contract} is a tuple $\langle  \ALS, \PUH, \CODE \rangle $, where
$\ALS$ is the alias of the contract, $\PUH$ is its public hash, and
$\CODE$ is the code of the contract. 
\end{definition}

\begin{definition}%[Manager]
A \emph{manager} manages a single account. It is represented by a
tuple $\langle  \PUK, \PKH, \BAL, \COU \rangle $, where  $\PUK$ is the
public key of an account, $\PKH$ is its public key hash, $\BAL$ is its
balance and $\COU$ is its counter whose form is a pair $(n, b)$, where $n$ is a natural number and ${b}$
is a boolean value.  
\end{definition}

\begin{definition}%[Contractor]
  A \emph{contractor} manages a smart contract. It is
  represented by a tuple
  $\langle \PUH, \BAL, \CODE, \STORAGE \rangle $, where $\PUH$ is the
  public key hash of the contract, $\BAL$ is its current balance, $\CODE$ is its
  code, and $\STORAGE$ is its current storage.
\end{definition}

\begin{definition}%[Operation]
  \emph{Operations} are defined by the following grammar:
  \begin{align*}
    \OP &::= \TRANSFER[\STRING]\NTEZ\PKH{\PKH'}\MTEZ
    \\&\mid \ORIGINATE\ID\NTEZ\PKH\CODE\STRING\MTEZ
    % \\&\mid transfer $\mathbf{n}$ from $\PKH$ to  $\PUH$ arg $\mathbf{s}$ fee $\mathbf{m}$
  \end{align*}
%\\$\mid$ register key $\PKH$ as delegate fee $\mathbf{m}$ 
%\\$\mid$ set delegate for $\PKH$ to $\PKH'$  fee $\mathbf{m}$ 
%\\$\mid$ withdraw delegate from $\PKH$ fee $\mathbf{m}$ 
\end{definition}

\begin{definition}%[Query]
A \emph{query} is defined by the following grammar:
\begin{align*}
  \QRY & ::= \GETBALANCE {\PKH / \PUH}
  \\&\mid \GETSTATUS\OPH
  \\&\mid \GETSTORAGE\PUH
  \\&\mid \GETCODE\PUH 
  \\&\mid \GETPUBLICKEY\PKH
  \\&\mid \GETCOUNTER\PKH
\end{align*}

@@

\end{definition}
 \begin{definition}%[State of a node]
   The \emph{state of a node} is a tuple
   $\NODE = [\ACCOUNTS, \OPERATIONS, \CONTRACTS]$ where $\ACCOUNTS$ is a set of accounts,
   $\OPERATIONS$ a set of operations, and $\CONTRACTS$  a set of contracts. 
\end{definition}

When an operation is injected in a node, it enters a \emph{pending pool}
(and is called a \emph{pending operation}). 
 \begin{definition}%[Pending operation]
A \emph{pending operation} is a tuple  $\langle  \OP, \OPH, \TIME
\rangle $, where $\OP$ is an operation, $\OPH$ is the operation hash,
and $\TIME$ is the time when the operation was injected. 
\end{definition}
After some time, a pending operation may be included in the blockchain as an accepted operation.
%Let \textit{P} is the set of pending operations.
 \begin{definition}%[Accepted operation]
An \emph{accepted operation}  is a tuple $\langle  \OP, \OPH, \TIME \rangle
$, where $\OP$ is an operation, $\OPH$ is the operation hash, and
$\TIME$ is the time when it was included in the blockchain. 
\end{definition}

\begin{definition}%[Blockchain]
  The \emph{state of a blockchain} is a tuple
  $[\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$ where
  $\PENDING$ is a set of pending operations,  $\ACCEPTED$ is a set
  of accepted operations, $\MANAGERS$ is a set of managers,
  $\CONTRACTORS$ is a set of contractors, and $\TIME$ is the current time. 
\end{definition}

\begin{definition}%[Blockchain system]
A \emph{blockchain configuration} is a pair
$ \NODE \| \BLOCKCHAIN$ where
\fxnote[inline]{Should the model contain multiple nodes?}
\begin{enumerate}
\item $\NODE = [\ACCOUNTS, \OPERATIONS, \CONTRACTS]$ is the state of a node, and
\item $\BLOCKCHAIN = [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$ is the state of a blockchain 
  such that $\forall c \in \ACCOUNTS \implies \exists k\in \MANAGERS, k.\PKH = c.\PKH$
  and $\forall s \in \CONTRACTS \implies \exists p \in \CONTRACTORS, s.\PUH = p.\PUH$.
\end{enumerate}
\end{definition}

\clearpage{}
\section{Rules}

@@

\begin{mathpar}
  \inferrule[Node-Transfer]
  {\CHECKACC (\PUK, \ACCOUNTS) \\
    \OP = \TRANSFER[\STRING]\NTEZ\PUK{\PUK'}\MTEZ
  }{
    [\ACCOUNTS, \OPERATIONS, \CONTRACTS]
    \NodeTrans
    [\ACCOUNTS, \OP:: \OPERATIONS, \CONTRACTS]
  }

  \inferrule[Node-Originate]
  {\CHECKACC (\PUK, \ACCOUNTS) \\
    \CHECKID (\ID, \CONTRACTS) \\
    \OP = \ORIGINATE\ID\NTEZ\PUK\CODE\STRING\MTEZ
  }{
    [\ACCOUNTS, \OPERATIONS, \CONTRACTS]
    \NodeTrans 
    [\ACCOUNTS, \OP :: \OPERATIONS, \CONTRACTS]
  }

  \inferrule[Node-System]
  {\NODE \NodeTrans \NODE'}
  { {\NODE \| \BLOCKCHAIN} \SystemTrans {\NODE'\| \BLOCKCHAIN}}

  \inferrule[Block-System]
  {\BLOCKCHAIN \BlockTrans \BLOCKCHAIN'}
  { {\NODE \| \BLOCKCHAIN} \SystemTrans {\NODE\| \BLOCKCHAIN'}}
\end{mathpar}

@@

\begin{equation}{}
\frac{\text{$\neg$ checkPub(\MANAGERS, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow$ }\\
\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 6 [included]:
\begin{mathpar}
  \inferrule[Block-Accept]{
    % \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
    \TIME'-\TIME < 60
  }{
    {[\Angle{\OP,\OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
      \CONTRACTORS, \TIME']}
    \BlockTrans 
    {[\PENDING, \Angle{\OP,\OPH,\TIME'} :: \ACCEPTED, \MANAGERS,
      \CONTRACTORS, \TIME'+1]}
  }
\end{mathpar}
Rule 7 [timeout]:
\begin{mathpar}
  \inferrule[Block-Timeout]{
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
    \TIME'-\TIME \ge 60
  }{
    {[\Angle{\OP,\OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
      \CONTRACTORS, \TIME']}
    \BlockTrans
    {[\PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS, \PUK, \FALSE),
      \CONTRACTORS, \TIME']}
  }
\end{mathpar}

@@

\begin{mathpar}
  \inferrule[Block-Originate]{
    \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
    \CHECKCOU (\MANAGERS, \PUK) \\
    \CHECKPRG (\CODE, \STRING) \\\\
    \ORIG = \ORIGINATE\ID\NTEZ\PUK\CODE\STRING\MTEZ 
  }{
    \Angle{[
      \ACCOUNTS, \ORIG :: \OPERATIONS, \CONTRACTS
      ], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]} \to \\
    \Angle{[\ACCOUNTS, \OPERATIONS, \CONTRACTS],
      [\Angle{\ORIG,\TIME} :: \PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS,\PUK,\TRUE), \CONTRACTORS, \TIME]}
  }
\end{mathpar}
% \begin{equation}{}
% \frac{\text{checkBal(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ \text{checkPrg($code, s$)}}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{ :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] $\rangle \rightarrow \langle$ [\ACCOUNTS, \OPERATIONS, \CONTRACTS],} \text{[(originate contract ${id}$ transferring ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: \PENDING, \ACCEPTED, updateCou(\MANAGERS, $pkh$, True), \CONTRACTORS, \TIME] $\rangle$}}} 
% \end{equation}
~\\
~\\
Rule 3 [rejected of code]:

@@

\begin{equation}{}
\frac{\text{$\neg$ checkBal(\MANAGERS, $pkh, n, m$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow \langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS],} \text{[\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 6 [included]:
\begin{mathpar}
  \inferrule[Block-Accept]{
    \OP = \ORIGINATE\ID\NTEZ\PUK\CODE\STRING\MTEZ \\
    \OPH = \GENERATEHASH (\ID,\CODE,\STRING,\TIME') \\
    \TIME'-\TIME < 60
  }{
    \Angle{[\ACCOUNTS, \OPERATIONS, \CONTRACTS],
      [\Angle{\OP,\TIME} :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME']}
    \SystemTrans \\
    \langle
      [\ACCOUNTS, \OPERATIONS, \Angle{\ID, \OPH, \CODE} ::\CONTRACTS],
      \\
      [\PENDING, \Angle{\OP, \TIME'} :: \ACCEPTED, \UPDATESUCC
      (\MANAGERS, \PUK, \NTEZ, \MTEZ), \Angle{\OPH, \GETSTORAGE
      (\CODE,\STRING)} :: \CONTRACTORS, \TIME'+1]
    \rangle
  }
\end{mathpar}

% \begin{equation}{}
% \frac{}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, \OPERATIONS,
% \CONTRACTS], [$<$ (originate contract ${id}$ transferring  ${n}$
% from ${pkh}$ running } \\ 
% \text{${code}$ init ${s}$), \TIME $>$ :: \PENDING, \ACCEPTED,
% \MANAGERS, \CONTRACTORS, \TIME' ]$\rangle \rightarrow
% \langle$[\ACCOUNTS, \OPERATIONS,($< id$, } \\ 
% \text{generateHash($id, code, s$, \TIME'), $code >$ :: \CONTRACTS)],
%  [\PENDING, $<$ (originate contract ${id}$ } \\
% \text{transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$), \TIME' $>$ :: \ACCEPTED, updateSucc(\MANAGERS, } \\
% \text{$puk, n, m$), ($<$ generateHash($id, code, s$, \TIME'), $n, code$, } \\
%  \text{getStorage($code, s$) $>$) :: \CONTRACTORS), \TIME' + 1]$\rangle$}}} 
% \end{equation}
~\\
Rule 7 [timeout]:
\begin{mathpar}
  \inferrule[Block-Timeout]{
    \OP = \ORIGINATE\ID\NTEZ\PUK\CODE\STRING\MTEZ \\
    \TIME'-\TIME \ge 60
}{
    %\Angle{[\ACCOUNTS, \OPERATIONS, \CONTRACTS],
      [\Angle{\OP,\TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
      \CONTRACTORS, \TIME']
    %}
    \BlockTrans
    % \Angle{[\ACCOUNTS, \OPERATIONS, \CONTRACTS],
      [\PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS,\PUK,\FALSE), \CONTRACTORS, \TIME']
    % }
}
\end{mathpar}
% \begin{equation}{}
% \frac{\text{\TIME' - \TIME $\ge$ 60}}{\parbox{4.2in}{\text{[$<$
% (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running
% ${code}$ init ${s}$) $>$ } \\ 
% \text{:: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ]
% $\rightarrow$[\PENDING, \ACCEPTED, updateCou(\MANAGERS, $puk$,
% False), \CONTRACTORS, \TIME']}}}  
% \end{equation}
~\\
~\\
B. \textbf{Transfer}
\\
~\\
Rule 1 [proposal]:
